\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{classic}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}

\firstname{Jingyu}
\lastname{Zhou}
\email{jy\_zhou@sjtu.edu.cn}
\phone{189-9065-8207}

\begin{document}
\makecvtitle

\section{Education}
\cventry{Sept. 2023 -- Present}{Artificial Intelligence}{Shanghai Jiao Tong University (SJTU)}{Minhang, Shanghai}
{GPA: 4.04/4.30, Rank: 4/95}{}
\cventry{Sept. 2023 -- Present}{Zhiyuan Honor Program}{Shanghai Jiao Tong University}{Minhang, Shanghai}
{Top 10\% of SJTU with advanced coursework}{}

\section{Experience}
\cventry{Jan. 2025 -- Present}{Research Intern}{GAIR, SJTU \& Qing Yuan Research Institute}{Minhang, Shanghai}{}
{
\begin{itemize}
    \item Proposed redefining modalities based on task-specific requirements instead of sensory modalities
    \item Joined a research team focused on multimodal machine learning, emphasizing Large Language Models (LLMs)
\end{itemize}
}

\cventry{Dec. 2024 -- Present}{Research Intern}{IPADS, SJTU}{Minhang, Shanghai}{}{}

\cventry{Sept. 2024 -- Jan. 2025}{Research Intern}{RHOS, SJTU \& Qing Yuan Research Institute}{Minhang, Shanghai}{}{}

\cventry{Feb. 2024 -- Sept. 2024}{Research Intern}{X-LANCE, SJTU}{Minhang, Shanghai}
{
\begin{itemize}
    \item Prepared tutorial report on TTS Based on Discrete Representations for NCMMSC 2024
    \item Conducted comparative analysis of TTS models, highlighting discrete representations' performance
\end{itemize}
}

\section{Honors and Awards}
\cventry{2024}{Shanghai Scholarship}{Top 2\% of students in Shanghai}{}{}{}
\cventry{2023 \& 2024}{Zhiyuan Honors Scholarship}{SJTU}{Top 5\% of Zhiyuan Honor Program students}{}{}
\cventry{2024}{Merit Scholarship, B level}{SJTU}{Top 5\% of students}{}{}

\section{Projects}
\cventry{Jan. 2024 -- Present}{aiTour}{}{}
{
\begin{itemize}
    \item Developed open-source resource for AI self-learners
    \item Public repository with over 2000 views
\end{itemize}
}

\section{Courses}
\cvline{A+ Courses}{Program Design(Honor), Discrete Math(Honor), Linear Algebra(Honor), Math Analysis(Honor), Artificial Intelligence Problem Solving and Practice, Data Structure(Honor), Digital Electronics, Programming Practices of Artificial Intelligence, Physical Education}

\cvline{Extracurricular Courses}{UCB CS61a, UCB CS61b, Stanford CS229, Stanford CS224n, Stanford CS236, University of Michigan EECS 498.008, MIT RES.6-012}

\cvline{Planning to Take}{CMU 15-213, MIT 6.S081}

\section{Skills \& Interests}
\cvline{Skills}{Python(Pytorch, numpy), Probability, Machine Learning, Deep Learning, Basic Use of Linux}
\cvline{Interests}{Natural Language Processing, (Multimodal) Machine Learning}

\end{document}